lab_notebook

### 2018-12-21 draft_figures_12.18.18.Rmd
diagnostics

>>>>

## run diagnostics

##Diagnostics

##run above chunk to get gdp_rightsbased df not the old csv file that is now archived in data folder

diagnostics <- gdp_rightsbased %>%
  mutate(management = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    turf == TRUE ~ "2",
    itq == FALSE | iq == FALSE | ivq == FALSE | turf == FALSE ~ "0"
    )) %>%
  select(Country, gdp_center, SpeciesCat, management)

#diagnostics wont run with non-numeric?
diagnostics$SpeciesCat <- as.numeric(diagnostics$SpeciesCat)
diagnostics$management <- as.numeric(diagnostics$management)

#2= gdp; 4= turf; 5 = SpeciesCat; 23 = itq; 24= ivq; 25 = iq; 26= binary rights based
pairs(diagnostics[2:4])

#pearson's r correlations
cor(diagnostics[2:4])

#run chi square?

### 2018-12-21 lab_notebook.Rmd
diagnostics

#closer look at corbett's data
```{r}
Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")

corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]

corbette_fisheries <- corbette_recent %>%
  select(assess_id_short, year, speciescat, iq, itq, ivq, coop, turf)%>%
  filter(itq != "NA" & iq != "NA" & ivq != "NA" )

fisheries_with_turfs <- corbette_fisheries %>%
  filter(turf != "FALSE")

fisheries_with_itq <- corbette_fisheries %>%
   filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" )

@@

###JULIETTE: check why the fisheries recent only has FALSE for turfs and no TRUEs

@@

#Update Projection with RAM
projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")

separate_projection <- projection_updated%>% 
  separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))

@@

fishery_itq_simple <- fisheries_with_itq %>%
  select(assess_id_short,iq, itq, ivq, turf )

@@

recent_pre2016 <- ITQ_projection_merge %>%
  filter(Year.x <= "2016")

fisheries_recent_1 <- setDT(recent_pre2016)[,.SD[which.max(Year.x)],keyby=assess_id_short]

fisheries_recent <- fisheries_recent_1 %>%
  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq, turf)

#fisheries_recent <- write.csv(fisheries_recent, file = "fisheries_recent.csv")

@@

@@

fisheries_KOBE_ram <- fisheries_recent %>%
  filter(Dbase == "RAM") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "0"]<- "No ITQ"
fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "1"]<- "ITQ"

@@

@@

F_B_graph <- ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(0, 2.5)+
  xlim(0, 2.5)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("KOBE Plot:  All Fisheries")

## adding turf information to upside projection (use fisheries recent?)
```{r}

@@

fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    ))

turfs <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
no_itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")

@@

turf_only <- turf_itq_isscaap %>%
  select(SciName, Country, turf, SpeciesCat) %>%
  filter(SpeciesCat != 91) %>%
  filter(SpeciesCat != 92)

fisheries_recent_generousturf_1 <- fisheries_recent %>%
  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)%>%
  filter(SpeciesCat.x != 91) %>%
  filter(SpeciesCat.x != 92)

@@

>>>>

#Pulling out information about ITQs/TURFs in Corbette Data to apply to upside data
```{r}

Countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")

#new dataframw with just most recent year of data for each fishery
corbette_recent <- setDT(Countries_ITQ)[,.SD[which.max(year)],keyby=assess_id_short]

#filter out the fisheries with no data on itqs or turfs
corbette_fisheries <- corbette_recent %>%
  select(assess_id_short, year, speciescat, iq, itq, ivq, coop, turf)%>%
  filter(itq != "NA" & iq != "NA" & ivq != "NA")%>%
  filter(turf != "NA" )

#new data frame with just data on fisheries with itqs
fisheries_with_itq <- corbette_fisheries %>%
   filter(itq == "TRUE" | iq == "TRUE" | ivq == "TRUE" | turf == "TRUE" )

@@

@@

#Update Projection with RAM
projection_updated <- join(ram, projection_data, by = c("CommName", "Year"), type = "full")
##note: RAM data has some fisheries not in the projection data, thus adding new fisheries to the upside projection data

#separate and unit functions to create a shorter version of the stock assessment ID to merge with corbette ITQ/TURF data later
separate_projection <- projection_updated%>% 
  separate(IdOrig, c("agency", "stock", "t0", "tf", "data_enterer"))

@@

#merge corbette's data on ITQ/Turf implemented or not for each fishery
fishery_itq_simple <- fisheries_with_itq %>%
  select(assess_id_short,iq, itq, ivq, turf )

@@

#filter out data post 2016 because we know that those are projected/modeled data not recorded
recent_pre2016 <- ITQ_projection_merge %>%
  filter(Year.x <= "2016")

#keep only info on most recent year for each fishery  
fisheries_recent_1 <- setDT(recent_pre2016)[,.SD[which.max(Year.x)],keyby=assess_id_short]

#select the columns we are interested in
fisheries_recent <- fisheries_recent_1 %>%
  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq, turf)

#write dataframe to csv file
#fisheries_recent <- write.csv(fisheries_recent, file = "fisheries_recent.csv")

@@

#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.

@@

#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"

#only looking at fisheries data that come from RAMS database
# creating new column called "rightsbased" where 1 = ITQ and 0 = No ITQ
fisheries_KOBE_ram <- fisheries_recent %>%
  filter(Dbase == "RAM") %>%
  mutate(rightsbased = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0"))

#graphing logistics
fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "0"]<- "No ITQ"
fisheries_KOBE_ram$rightsbased[fisheries_KOBE_ram$rightsbased == "1"]<- "ITQ"

@@

#F_B_graph
ggplotly(F_B_graph_RAM)

#read in data: this is updated projection data (updated using RAMs) and Corbett's ITQ/Turf data applied to each fishery. only data for most recent year for each fishery is represented.
fisheries_recent <- read_csv("data/fisheries_recent.csv")

#assuming that when no data is avaliable on the fishery inregardes to ITQ or Turfs that means there are none
fisheries_recent$itq[is.na(fisheries_recent$itq)] <- "FALSE"
fisheries_recent$ivq[is.na(fisheries_recent$ivq)] <- "FALSE"
fisheries_recent$iq[is.na(fisheries_recent$iq)] <- "FALSE"
fisheries_recent$turf[is.na(fisheries_recent$turf)] <- "FALSE"

#graphing logistics
F_B_graph <- ggplot(data = fisheries_KOBE, aes( x=BvBmsy, y=FvFmsy, colour= rightsbased, size = Catch ))+
  geom_point()+
  labs(x = "B/Bmsy", y= "F/Fsmy") +
  theme_minimal()+
  theme(legend.title=element_blank())+
  ylim(0, 2.5)+
  xlim(0, 2.5)+
  geom_hline(aes(yintercept=1))+
  geom_vline(aes(xintercept=1))+
  ggtitle("KOBE Plot:  All Fisheries")

@@

## adding turf information to upside projection(ie: fisheries_recent)
```{r}

#load in data for turf/itq only projection
turf_itq_isscaap <- read_csv("data/turf_itq_isscaap.csv")

@@

#merge the most recent data on each fishery with turf data
fisheries_recent_generousturf <- merge(fisheries_recent_generousturf_1, turf_only, by = c("Country", "SciName")) #, all = "TRUE")

#assuming that when no data is present for itqs/turf that means there are none
fisheries_recent_generousturf$turf[is.na(fisheries_recent_generousturf$turf)] <- "FALSE"
fisheries_recent_generousturf$itq[is.na(fisheries_recent_generousturf$itq)] <- "FALSE"
fisheries_recent_generousturf$ivq[is.na(fisheries_recent_generousturf$ivq)] <- "FALSE"
fisheries_recent_generousturf$iq[is.na(fisheries_recent_generousturf$iq)] <- "FALSE"

fisheries_recent_generousturf_rightsbased <- fisheries_recent_generousturf %>%
  mutate(rightsbased = case_when(
    turf == TRUE ~ "2",
    itq == FALSE & iq == FALSE & ivq == FALSE ~ "0",
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1"
    ))

#create dfs for turf, itq, and no itq fisheries to calculate the sum of each
#NOTE to rememeber: the data from these fisheries are the most recent numbers we have. they are not all in the same year 
turfs <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "2")
itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "1")
no_itq <- filter(fisheries_recent_generousturf_rightsbased, rightsbased == "0")

@@

turf_only <- turf_itq_isscaap %>%
  select(SciName, Country, turf, SpeciesCat)

fisheries_recent_generousturf_1 <- fisheries_recent %>%
  select(Country, assess_id_short, Year.x, CommName, Biomass, Catch, BvBmsy, FvFmsy, Dbase, SciName, IdLevel, SpeciesCat.x, Profits, MSY, Price, g, k, c, phi, itq, ivq, iq)

@@

##Diagnostics

##run above chunk to get gdp_rightsbased df not the old csv file that is now archived in data folder

diagnostics <- gdp_rightsbased %>%
  mutate(management = case_when(
    itq == TRUE | iq == TRUE | ivq == TRUE ~ "1",
    turf == TRUE ~ "2",
    itq == FALSE | iq == FALSE | ivq == FALSE | turf == FALSE ~ "0"
    )) %>%
  select(Country, gdp_center, SpeciesCat, management)

#diagnostics wont run with non-numeric?
diagnostics$SpeciesCat <- as.numeric(diagnostics$SpeciesCat)
diagnostics$management <- as.numeric(diagnostics$management)

#2= gdp; 4= turf; 5 = SpeciesCat; 23 = itq; 24= ivq; 25 = iq; 26= binary rights based
pairs(diagnostics[2:4])

#pearson's r correlations
cor(diagnostics[2:4])

#run chi square?

```
## MPA stuff
